Can We Crunch the Social Graph on the Cheap?

### 2011-01-25 doc/hotpar2011/softxmt-hotpar2011.tex
modified:   softxmt-hotpar2011.tex

Our programming model partitions the address space into a shared
global shared address space and per node private address spaces.
Locality may be exploited directly by the programmer in the node
private address spaces, just as in a conventional cache-coherent
multiprocessor node.  In contrast, the global space is explicitly
uncached.  There, every processor can access any word of memory
directly via its unique global address.

Whereas in the PGAS model coherency of global copies is implictly
maintained across the system, we forego caching of globally shared
data.  A node can exploit locality within a chunk of data stored in
the global space only by first copying it into the node's local space.
In this way, a node can access data at random across the system while
incurring no hardware coherence overhead: consistency is enforced by
our mechanisms for explicit global synchronization.

>>>>

Our shared-memory programming model partitions the overall address
space into a global shared address space and per node private address
spaces.  Locality may be exploited directly by the programmer in the
node private address spaces, just as in a conventional cache-coherent
multiprocessor node.  In contrast, the global space is explicitly
uncached.  There, every processor can access any word of memory
directly via its unique global address.

Whereas in the PGAS model coherency of global copies is implictly
maintained across the system, we forego caching of globally shared
data.  A node can exploit temporal locality of data stored in
the global space only by first copying it into the node's local space.
In this way, a node can access data at random across the system while
incurring no hardware coherence overhead: consistency is enforced by
our mechanisms for explicit global synchronization.
